paper2_resistance_mechanisms_mixtures

### 2016-06-27 inst/documents/paper1_results_figs_rr.Rmd
renamed rr_restoration

# Figures for paper 1 after change to using rr_advantage instead of selection coeff from sensi analysis
# version 1 - in progress

@@

  #hardcode which variables to include in analysis to keep it simple and transparent
  #treePredictors <- c('P_1','P_2','exposure','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  #14/6/16 change to rr_advantage
  treePredictors <- c('P_1','P_2','exposure','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','rr_advantage_I1','rr_advantage_I2')

@@

  #14/6/16 rr_advantage these not to be used anymore
  #rownames(treeInput)[rownames(treeInput)=="s.RR1_A0"] <- "selection_coef_allele1"
  #rownames(treeInput)[rownames(treeInput)=="s.RR2_0B"] <- "selection_coef_allele2"

@@

  #create a curtisInputs dataframe for use later
  curtisInputs <- data.frame("exposure"=0.9,
                             "effectiveness_insecticide1"=0.73,
                             "effectiveness_insecticide2"=1,
                             "effectiveness_added"=1.73,                             
                             "start_freq_allele1"=0.01,
                             "start_freq_allele2"=0.01,
                             "dominance_allele1"=0.17,
                             "dominance_allele2"=0.0016,
                             "dominance_added"=0.1716,                             
                             # 14/6/16 rr_advantage = s / effectiveness
                             #"selection_coef_allele1"=0.23,
                             #"selection_coef_allele2"=0.43,
                             "rr_advantage_I1"=0.23/0.73,
                             "rr_advantage_I2"=0.43/1,                             
                             "male_exposure_prop"=1,
                             "correct_mix_deploy"=1,
                             "resist_start_lo_div_hi"=1,
                             "resist_start_1_div_2"=1)

>>>>

# Figures for paper 1 after change to using rr_restoration instead of selection coeff from sensi analysis
# version 1 - in progress

@@

  #hardcode which variables to include in analysis to keep it simple and transparent
  #treePredictors <- c('P_1','P_2','exposure','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  #14/6/16 change to rr_restoration
  treePredictors <- c('P_1','P_2','exposure','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','rr_restoration_ins1','rr_restoration_ins2')

@@

  #14/6/16 rr_restoration these not to be used anymore
  #rownames(treeInput)[rownames(treeInput)=="s.RR1_A0"] <- "selection_coef_allele1"
  #rownames(treeInput)[rownames(treeInput)=="s.RR2_0B"] <- "selection_coef_allele2"

@@

  #create a curtisInputs dataframe for use later
  curtisInputs <- data.frame("exposure"=0.9,
                             "effectiveness_insecticide1"=0.73,
                             "effectiveness_insecticide2"=1,
                             "effectiveness_added"=1.73,                             
                             "start_freq_allele1"=0.01,
                             "start_freq_allele2"=0.01,
                             "dominance_allele1"=0.17,
                             "dominance_allele2"=0.0016,
                             "dominance_added"=0.1716,                             
                             # 14/6/16 rr_restoration = s / effectiveness
                             #"selection_coef_allele1"=0.23,
                             #"selection_coef_allele2"=0.43,
                             "rr_restoration_ins1"=0.23/0.73,
                             "rr_restoration_ins2"=0.43/1,                             
                             "male_exposure_prop"=1,
                             "correct_mix_deploy"=1,
                             "resist_start_lo_div_hi"=1,
                             "resist_start_1_div_2"=1)

### 2016-06-27 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
renamed rr_restoration

## using rr_advantage instead of selection coefficient

@@

#curtis_f2 with P_1 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.49 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , rr_advantage_I1=0.23/0.73, rr_advantage_I2 = 0.43/1, addCombinedStrategy=FALSE )

#curtis_f2 with P_2 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.01 , P_2 = 0.49 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , rr_advantage_I1=0.23/0.73, rr_advantage_I2 = 0.43/1, addCombinedStrategy=FALSE )

>>>>

## using rr_restoration instead of selection coefficient

@@

#curtis_f2 with P_1 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.49 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , rr_restoration_ins1=0.23/0.73, rr_restoration_ins2 = 0.43/1, addCombinedStrategy=FALSE )

#curtis_f2 with P_2 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.01 , P_2 = 0.49 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , rr_restoration_ins1=0.23/0.73, rr_restoration_ins2 = 0.43/1, addCombinedStrategy=FALSE )

### 2016-06-27 inst/documents/paper2_resistance_mechanisms_mixtures.Rmd
renamed rr_restoration

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.2,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.8,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

@@

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

@@

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.2, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.8, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.2,
                      rr_advantage_I2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.5,
                      rr_advantage_I2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_advantage_I1 = 0.8,
                      rr_advantage_I2 = 0.5 )

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=rr_advantage_I1)) + 
         labs(colour = "selective advantage") +
         coord_trans(y = "log10") +   
         geom_point() #show.legend=FALSE) +

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 1. All control inputs equal at 0.5")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 2. Effectiveness of insecticide1 increased from 0.5 to 0.9")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.9 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 3. Effectiveness of both insecticides 0.9")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 4. Dominance of insecticide1 0.9")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.9 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 5. Dominance of both insecticides 0.9")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.1 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 6. Selective advantage of insecticide1 0.1")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.1 , rr_advantage_I2 = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 7. Selective advantage of both insecticides 0.1")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.1 , rr_advantage_I2 = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 8. Selective advantage of both insecticides 0.1, effectiveness to 0.7")
```

#cool contrast between these scenarios modifying effectiveness and rr_advantage in which all defaults set to 0.5 except
TODO incorporate this into text above

#AA effectiveness I1 to 0.8 causes mixture to be slower, although I1 is faster it protects I2 in mixture, making mixture slower
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. AA. effectiveness to 0.8")
```

#BB rr advantage I1 to 0.8 sequential remains slower, although I1 is faster as in previous it provides less protection to I2 in the mixture
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.8 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. BB rr_advantage I1 0.8")
```

#CC rr advantage I2 to 0.2 sequential remains slower (just), I2 slower than I1 in mixture similar to AA but receives less protection in mixture
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.2 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. CC. rr_advantage I2 0.2")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 9. Exposure 0.9")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 10. Effectiveness 0.7, sequence favoured")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , rr_advantage_I1 = 0.5 , rr_advantage_I2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 11. Effectiveness 0.7, Exposure 0.9, mixture favoured")
```

>>>>

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.2,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.8,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

@@

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

@@

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      exposure = exposure, #used for post-run analysis
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.2, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.8, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

@@

  i1 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.2,
                      rr_restoration_ins2 = 0.5 )

  i2 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.5,
                      rr_restoration_ins2 = 0.5 )

  i3 <- setInputOneScenario( max_gen = 500,
                      h.RS1_A0 = 0.5, 
                      h.RS2_0B = 0.5,
                      a = a,
                      phi.SS1_A0 = 0.5,
                      phi.SS2_0B = 0.5,
                      rr_restoration_ins1 = 0.8,
                      rr_restoration_ins2 = 0.5 )

@@

  print( ggplot(df_resist, aes(x=generation, y=resistance, colour=rr_restoration_ins1)) + 
         labs(colour = "selective advantage") +
         coord_trans(y = "log10") +   
         geom_point() #show.legend=FALSE) +

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 1. All control inputs equal at 0.5")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 2. Effectiveness of insecticide1 increased from 0.5 to 0.9")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.9 , phi.SS2_0B = 0.9 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 3. Effectiveness of both insecticides 0.9")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 4. Dominance of insecticide1 0.9")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.9 , h.RS2_0B = 0.9 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 5. Dominance of both insecticides 0.9")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.1 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 6. Selective advantage of insecticide1 0.1")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.1 , rr_restoration_ins2 = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 7. Selective advantage of both insecticides 0.1")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.1 , rr_restoration_ins2 = 0.1 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 8. Selective advantage of both insecticides 0.1, effectiveness to 0.7")
```

#cool contrast between these scenarios modifying effectiveness and rr_restoration in which all defaults set to 0.5 except
TODO incorporate this into text above

#AA effectiveness I1 to 0.8 causes mixture to be slower, although I1 is faster it protects I2 in mixture, making mixture slower
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. AA. effectiveness to 0.8")
```

#BB rr advantage I1 to 0.8 sequential remains slower, although I1 is faster as in previous it provides less protection to I2 in the mixture
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. BB rr_restoration I1 0.8")
```

#CC rr advantage I2 to 0.2 sequential remains slower (just), I2 slower than I1 in mixture similar to AA but receives less protection in mixture
```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.2 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. CC. rr_restoration I2 0.2")
```

@@

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 9. Exposure 0.9")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 10. Effectiveness 0.7, sequence favoured")
```

```{r, eval=TRUE, echo=FALSE, fig.height=4}
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.9 , phi.SS1_A0 = 0.7 , phi.SS2_0B = 0.7 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('seq','','adapt','mix2') )
cat("Fig. 11. Effectiveness 0.7, Exposure 0.9, mixture favoured")
```
